---
title: "Case Study Lag Effect"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
setwd("~/binary_mrt/Case Study/lag effect")
library(readr)
load("imputation_list_daily_separated_no_mess_sep.RData")
# load("reduced_US_step_sleep_mood_daily_2018_full.RData")
# load("cleaned_reduced_intervention_data_full.RData")
IHSdata_2018 <- read_csv("IHSdata_2018.csv")
colnames(IHSdata_2018)[1] <- "USERID"
study_data = impute_list[[1]]
library(dplyr)
library(geepack)
library(tidyr)
library(ggplot2)
`%notin%` <- Negate(`%in%`)
```


## Direct Effect

```{r}
load("full_data_complete.RData")
source("C-WCLS.R")

dta = full_data_complete %>% 
  mutate(mood_week = ifelse(week_category == "mood",1,0),
         sleep_week = ifelse(week_category == "sleep",1,0),
         activity_week = ifelse(week_category == "activity",1,0),
         study_week_2 = study_week^2)

cluster_size = full_data_complete %>%
  distinct(USERID,INSTITUTION_STANDARD)%>%
  group_by(INSTITUTION_STANDARD)%>%
  count()

# cluster_size = dta %>%
#   distinct(USERID,Specialty,INSTITUTION_STANDARD)%>%
#   group_by(Specialty,INSTITUTION_STANDARD)%>%
#   count()

cluster_size$group_id = 1:nrow(cluster_size)

#dta$week_category = factor(as.character(dta$week_category),
#                            levels = c("sleep","mood","activity"))
dta$week_category_num = as.numeric(dta$week_category)


dta$NOTIFICATION_TYPE = factor(as.character(dta$NOTIFICATION_TYPE),
                            levels = c("no_message","life insight","tip"))
#unique(dta$NOTIFICATION_TYPE)
dta$NOTIFICATION_TYPE_num = as.numeric(dta$NOTIFICATION_TYPE)

# User_specialty = dta %>%
#   select(USERID,Specialty,INSTITUTION_STANDARD)%>%
#   distinct()%>%
#   left_join(cluster_size[,c(1,2,4)], by = c("Specialty","INSTITUTION_STANDARD"))

User_specialty = dta %>%
  select(USERID,INSTITUTION_STANDARD)%>%
  distinct()%>%
  left_join(cluster_size[,c(1,3)], by = c("INSTITUTION_STANDARD"))

# construct the group structure
group = list()
group[["group_id"]] = as.matrix(User_specialty[,"group_id"])
group[["group size"]] = unname(table(group[["group_id"]]))
group[["#groups"]] = length(unique(group[["group_id"]]))
group[["id"]] = unique(group[["group_id"]])


dta$prob_A <- 3/8

dta = dta %>% group_by(USERID)%>% 
  mutate(Daily_complete_delta = lead(Daily_complete),
         NOTIFICATION_delta = lead(NOTIFICATION)) %>%
  drop_na(Daily_complete_delta,Daily_complete_delta)
```


```{r}
my_plot_data = as.data.frame(matrix(NA,nrow = 10,ncol = 7))
colnames(my_plot_data)= c("Index","Model-coef","est","SE","CI lower","CI upper","Method")

my_plot_data$Index = 1:nrow(my_plot_data)
my_plot_data$`Model-coef`=rep(c("Marginal-intercept","ModeratePrev-intercept","ModeratePrev-prev","ModerateDay-intercept","ModerateDay-day"),2) 
my_plot_data$Method =rep(c("ST","OTD"),each = 5) 
```


### analysis 1: Fully marginal

```{r}
control_vars <- c("DAILYprev","Day")
moderator_vars <- NULL

## Sequential Treatment
 
fit_wcls <- weighted_centered_least_square(
  dta = dta,
  group=group,
  id_varname = "USERID",
  decision_time_varname = "Day",
  treatment_varname = "NOTIFICATION",
  outcome_varname = "Daily_complete_delta",
  control_varname = control_vars,
  moderator_varname = moderator_vars,
  rand_prob_varname = "prob_A",
  rand_prob_tilde_varname = NULL,
  rand_prob_tilde = 3/8,
  avail_varname = NULL,
  estimator_initial_value = NULL,
  future_treatment = "ST"
)
 
fit_wcls_2 <- weighted_centered_least_square(
  dta = dta,
  group=group,
  id_varname = "USERID",
  decision_time_varname = "Day",
  treatment_varname = "NOTIFICATION",
  outcome_varname = "Daily_complete_delta",
  control_varname = control_vars,
  moderator_varname = moderator_vars,
  rand_prob_varname = "prob_A",
  rand_prob_tilde_varname = NULL,
  rand_prob_tilde = 3/8,
  avail_varname = NULL,
  estimator_initial_value = NULL,
  future_treatment = "OTD"
)
```

### Direct Effect Estimation summary

#### Sequential Treatment

```{r warning=FALSE}
dta %>% group_by(NOTIFICATION) %>% summarise(m = mean(Daily_complete))
```

##### point estimation

```{r}
fit_wcls$beta_hat 
```

#####  SE
```{r}
fit_wcls$beta_se
```

##### adjusted SE
```{r}
fit_wcls$beta_se_adjusted 
```

##### 95% CI
```{r}
t_quantile <- qt(0.975, length(unique(dta$Specialty)) - 1 - 2) 
rbind(fit_wcls$beta_hat - t_quantile * fit_wcls$beta_se_adjusted,
      fit_wcls$beta_hat + t_quantile * fit_wcls$beta_se_adjusted)
```

##### p value
```{r}
2 * pt(abs(fit_wcls$beta_hat)/fit_wcls$beta_se_adjusted,df =length(unique(dta$Specialty)) - 1 - 2, lower.tail = FALSE) 
```


```{r include=FALSE}
my_plot_data[1,3:6] = c(fit_wcls$beta_hat,
             fit_wcls$beta_se_adjusted , 
             fit_wcls$beta_hat - t_quantile * fit_wcls$beta_se_adjusted,
             fit_wcls$beta_hat + t_quantile * fit_wcls$beta_se_adjusted)
```

#### Observed Treatment Distribution

##### point estimation

```{r}
fit_wcls_2$beta_hat 
```
##### adjusted SE
```{r}
fit_wcls_2$beta_se_adjusted 
```
##### 95% CI
```{r}
t_quantile <- qt(0.975, length(unique(dta$USERID)) - 1 - 2) 
rbind(fit_wcls_2$beta_hat - t_quantile * fit_wcls_2$beta_se_adjusted,
      fit_wcls_2$beta_hat + t_quantile * fit_wcls_2$beta_se_adjusted)
```

##### p value
```{r}
2 * pt(abs(fit_wcls_2$beta_hat)/fit_wcls_2$beta_se_adjusted,df = length(unique(dta$Specialty))- 1 - 2, lower.tail = FALSE) 
```


```{r include=FALSE}
my_plot_data[6,3:6] = c(fit_wcls_2$beta_hat,
             fit_wcls_2$beta_se_adjusted , 
             fit_wcls_2$beta_hat - t_quantile * fit_wcls_2$beta_se_adjusted,
             fit_wcls_2$beta_hat + t_quantile * fit_wcls_2$beta_se_adjusted)
```

### analysis 2: Add day-in-sutdy

```{r}
control_vars <- c("DAILYprev","Day")
moderator_vars <- c("Day")

## Sequential Treatment
 
fit_wcls <- weighted_centered_least_square(
  dta = dta,
  group=group,
  id_varname = "USERID",
  decision_time_varname = "Day",
  treatment_varname = "NOTIFICATION",
  outcome_varname = "Daily_complete_delta",
  control_varname = control_vars,
  moderator_varname = moderator_vars,
  rand_prob_varname = "prob_A",
  rand_prob_tilde_varname = NULL,
  rand_prob_tilde = 3/8,
  avail_varname = NULL,
  estimator_initial_value = NULL,
  future_treatment = "ST"
)


## Observed Treatment Distribution
 
fit_wcls_2 <- weighted_centered_least_square(
  dta = dta,
  group=group,
  id_varname = "USERID",
  decision_time_varname = "Day",
  treatment_varname = "NOTIFICATION",
  outcome_varname = "Daily_complete_delta",
  control_varname = control_vars,
  moderator_varname = moderator_vars,
  rand_prob_varname = "prob_A",
  rand_prob_tilde_varname = NULL,
  rand_prob_tilde = 3/8,
  avail_varname = NULL,
  estimator_initial_value = NULL,
  future_treatment = "OTD"
)
```

### Direct Effect Estimation summary

#### Sequential Treatment

##### point estimation

```{r}
fit_wcls$beta_hat 
```

#####  SE
```{r}
fit_wcls$beta_se
```

##### adjusted SE
```{r}
fit_wcls$beta_se_adjusted 
```

##### 95% CI
```{r}
t_quantile <- qt(0.975, length(unique(dta$Specialty)) - 1 - 2) 
rbind(fit_wcls$beta_hat - t_quantile * fit_wcls$beta_se_adjusted,
      fit_wcls$beta_hat + t_quantile * fit_wcls$beta_se_adjusted)
```

##### p value
```{r}
2 * pt(abs(fit_wcls$beta_hat)/fit_wcls$beta_se_adjusted,df =length(unique(dta$Specialty)) - 1 - 2, lower.tail = FALSE) 
```


```{r include=FALSE}
my_plot_data[4,3:6] = c(fit_wcls$beta_hat[1],
             fit_wcls$beta_se_adjusted[1] , 
             fit_wcls$beta_hat[1] - t_quantile * fit_wcls$beta_se_adjusted[1],
             fit_wcls$beta_hat[1] + t_quantile * fit_wcls$beta_se_adjusted[1])

my_plot_data[5,3:6] = c(fit_wcls$beta_hat[2],
             fit_wcls$beta_se_adjusted[2] , 
             fit_wcls$beta_hat[2] - t_quantile * fit_wcls$beta_se_adjusted[2],
             fit_wcls$beta_hat[2] + t_quantile * fit_wcls$beta_se_adjusted[2])


var_cor_2 = fit_wcls[["varcov_adjusted"]][4,5]
```



#### Observed Treatment Distribution

##### point estimation

```{r}
fit_wcls_2$beta_hat 
```
##### adjusted SE
```{r}
fit_wcls_2$beta_se_adjusted 
```
##### 95% CI
```{r}
t_quantile <- qt(0.975, length(unique(dta$USERID)) - 1 - 2)
rbind(fit_wcls_2$beta_hat - t_quantile * fit_wcls_2$beta_se_adjusted,
      fit_wcls_2$beta_hat + t_quantile * fit_wcls_2$beta_se_adjusted)
```

##### p value
```{r}
2 * pt(abs(fit_wcls_2$beta_hat)/fit_wcls_2$beta_se_adjusted,df = length(unique(dta$Specialty))- 1 - 2, lower.tail = FALSE) 
```


```{r include=FALSE}
my_plot_data[9,3:6] = c(fit_wcls_2$beta_hat[1],
             fit_wcls_2$beta_se_adjusted[1] , 
             fit_wcls_2$beta_hat[1] - t_quantile * fit_wcls_2$beta_se_adjusted[1],
             fit_wcls_2$beta_hat[1] + t_quantile * fit_wcls_2$beta_se_adjusted[1])

my_plot_data[10,3:6] = c(fit_wcls_2$beta_hat[2],
             fit_wcls_2$beta_se_adjusted[2] , 
             fit_wcls_2$beta_hat[2] - t_quantile * fit_wcls_2$beta_se_adjusted[2],
             fit_wcls_2$beta_hat[2] + t_quantile * fit_wcls_2$beta_se_adjusted[2])

var_cor_2_qian = fit_wcls_2[["varcov_adjusted"]][4,5]
```

### analysis 3: Add previous week's mood completion rate as a moderator

```{r}
control_vars <- c("DAILYprev","Day")
moderator_vars <- c("DAILYprev")

## Sequential Treatment
 
fit_wcls <- weighted_centered_least_square(
  dta = dta,
  group=group,
  id_varname = "USERID",
  decision_time_varname = "Day",
  treatment_varname = "NOTIFICATION",
  outcome_varname = "Daily_complete_delta",
  control_varname = control_vars,
  moderator_varname = moderator_vars,
  rand_prob_varname = "prob_A",
  rand_prob_tilde_varname = NULL,
  rand_prob_tilde = 3/8,
  avail_varname = NULL,
  estimator_initial_value = NULL,
  future_treatment = "ST"
)


## Observed Treatment Distribution
 
fit_wcls_2 <- weighted_centered_least_square(
  dta = dta,
  group=group,
  id_varname = "USERID",
  decision_time_varname = "Day",
  treatment_varname = "NOTIFICATION",
  outcome_varname = "Daily_complete_delta",
  control_varname = control_vars,
  moderator_varname = moderator_vars,
  rand_prob_varname = "prob_A",
  rand_prob_tilde_varname = NULL,
  rand_prob_tilde = 3/8,
  avail_varname = NULL,
  estimator_initial_value = NULL,
  future_treatment = "OTD"
)

```

### Direct Effect Estimation summary

##### point estimation

```{r}
fit_wcls$beta_hat 
```

#####  SE
```{r}
fit_wcls$beta_se
```

##### adjusted SE
```{r}
fit_wcls$beta_se_adjusted 
```

##### 95% CI
```{r}
t_quantile <- qt(0.975, length(unique(dta$Specialty)) - 1 - 2) 
rbind(fit_wcls$beta_hat - t_quantile * fit_wcls$beta_se_adjusted,
      fit_wcls$beta_hat + t_quantile * fit_wcls$beta_se_adjusted)
```

##### p value
```{r}
2 * pt(abs(fit_wcls$beta_hat)/fit_wcls$beta_se_adjusted,df =length(unique(dta$Specialty)) - 1 - 2, lower.tail = FALSE) 
```



```{r include=FALSE}
my_plot_data[2,3:6] = c(fit_wcls$beta_hat[1],
             fit_wcls$beta_se_adjusted[1] , 
             fit_wcls$beta_hat[1] - t_quantile * fit_wcls$beta_se_adjusted[1],
             fit_wcls$beta_hat[1] + t_quantile * fit_wcls$beta_se_adjusted[1])

my_plot_data[3,3:6] = c(fit_wcls$beta_hat[2],
             fit_wcls$beta_se_adjusted[2] , 
             fit_wcls$beta_hat[2] - t_quantile * fit_wcls$beta_se_adjusted[2],
             fit_wcls$beta_hat[2] + t_quantile * fit_wcls$beta_se_adjusted[2])

var_cor_3 = fit_wcls[["varcov_adjusted"]][4,5]
```


#### Observed Treatment Distribution

##### point estimation

```{r}
fit_wcls_2$beta_hat 
```
##### adjusted SE
```{r}
fit_wcls_2$beta_se_adjusted 
```
##### 95% CI
```{r}
t_quantile <- qt(0.975, length(unique(dta$USERID)) - 1 - 2)
rbind(fit_wcls_2$beta_hat - t_quantile * fit_wcls_2$beta_se_adjusted,
      fit_wcls_2$beta_hat + t_quantile * fit_wcls_2$beta_se_adjusted)
```

##### p value
```{r}
2 * pt(abs(fit_wcls_2$beta_hat)/fit_wcls_2$beta_se_adjusted,df = length(unique(dta$Specialty))- 1 - 2, lower.tail = FALSE) 
```


```{r include=FALSE}
my_plot_data[7,3:6] = c(fit_wcls_2$beta_hat[1],
             fit_wcls_2$beta_se_adjusted[1] , 
             fit_wcls_2$beta_hat[1] - t_quantile * fit_wcls_2$beta_se_adjusted[1],
             fit_wcls_2$beta_hat[1] + t_quantile * fit_wcls_2$beta_se_adjusted[1])

my_plot_data[8,3:6] = c(fit_wcls_2$beta_hat[2],
             fit_wcls_2$beta_se_adjusted[2] , 
             fit_wcls_2$beta_hat[2] - t_quantile * fit_wcls_2$beta_se_adjusted[2],
             fit_wcls_2$beta_hat[2] + t_quantile * fit_wcls_2$beta_se_adjusted[2])

var_cor_3_qian = fit_wcls_2[["varcov_adjusted"]][4,5]
```


```{r}
### first plot: forest plot

# labs <- plot_1$Method
# yi   <- plot_1$est
# sei  <- plot_1$SE
# 
# # Combine data into summary estimate
# res  <- rma(yi=yi, sei=sei, method="FE")
# # summary(res)
# 
# # Plot combined data
# forest(res, transf=exp, refline=1, xlab="relative risk (95%CI)", slab=labs, mlab="Summary Estimate")
#mtext(paste("Association p-value=",summary(res)$pval),side=3, line=-1)
#mtext(paste("Heterogeneity p-value=",summary(res)$QEp),side=3, line=-2.25)
```

```{r eval=FALSE, include=FALSE}
library(ggforestplot)
plot_1 = my_plot_data[c(1,6),]
forestplot(
  df = plot_1,
  name = Method,
  estimate = est,
  se = SE,
  logodds = T,
  xlab = "Relative Risk (95% CI)")
```

```{r}
plot_2 = my_plot_data[c(2,3,7,8),]

data = as.data.frame(matrix(NA, nrow = 200, ncol = 5))
colnames(data) = c("x","y","lower","upper","Method")
data$x = rep(seq(0,1,length.out = 100),2)
data$Method = rep(c("ST","OTD"),each = 100)

data$y[1:100] = exp(plot_2[1,3]+plot_2[2,3]*data$x[1:100])
data$y[101:200] = exp(plot_2[3,3]+plot_2[4,3]*data$x[101:200])


########## part 1
var_cor_cwcls = matrix(c((my_plot_data[2,"SE"])^2,var_cor_3,var_cor_3,(my_plot_data[3,"SE"])^2),nrow=2)

calculate_se = function(x) sqrt(t(c(1,x))%*%var_cor_cwcls%*%c(1,x))

se_cor = sapply(data$x[1:100],FUN=calculate_se)

t_quantile <- qt(0.975, length(unique(dta$Specialty)) - 1 - 2)

data$lower[1:100] = data$y[1:100] - t_quantile*data$y[1:100]*se_cor
data$upper[1:100] = data$y[1:100] + t_quantile*data$y[1:100]*se_cor


####### part2
var_cor_emee = matrix(c((my_plot_data[7,"SE"])^2,var_cor_3_qian,var_cor_3_qian,(my_plot_data[8,"SE"])^2),nrow=2)

calculate_se = function(x) sqrt(t(c(1,x))%*%var_cor_emee%*%c(1,x))

se_cor = sapply(data$x[101:200],FUN=calculate_se)

t_quantile <- qt(0.975, length(unique(dta$USERID)) - 1 - 2)
data$lower[101:200] = data$y[101:200] - t_quantile*data$y[101:200]*se_cor
data$upper[101:200] = data$y[101:200] + t_quantile*data$y[101:200]*se_cor


p<-ggplot(data=data, aes(x=x, y=y, colour=Method)) + geom_line()
p<-p+geom_ribbon(aes(ymin=lower, ymax=upper), linetype=2, alpha=0.1)+xlab("Prior Week Completion Rate")+ylab("Relative Risk")+
  theme_bw()+
    theme(axis.line = element_line(colour = "black"),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    panel.border = element_blank(),
    panel.background = element_blank()) +
    geom_hline(yintercept =1, linetype=2)+
    theme(axis.text=element_text(size=12),
        axis.title=element_text(size=14))#,face="bold")


######################################################



plot_3 = my_plot_data[c(4,5,9,10),]

data = as.data.frame(matrix(NA, nrow = 364, ncol = 5))
colnames(data) = c("x","y","lower","upper","Method")
data$x = rep(1:182,2)
data$Method = rep(c("ST","OTD"),each = 182)

data$y[1:182] = exp(plot_3[1,3]+plot_3[2,3]*data$x[1:182])
data$y[183:364] = exp(plot_3[3,3]+plot_3[4,3]*data$x[183:364])


########## part 1
var_cor_cwcls = matrix(c((my_plot_data[4,"SE"])^2,var_cor_2,var_cor_2,(my_plot_data[5,"SE"])^2),nrow=2)

calculate_se = function(x) sqrt(t(c(1,x))%*%var_cor_cwcls%*%c(1,x))

se_cor = sapply(data$x[1:182],FUN=calculate_se)

t_quantile <- qt(0.975, length(unique(dta$Specialty)) - 1 - 2)

data$lower[1:182] = data$y[1:182] - t_quantile*data$y[1:182]*se_cor
data$upper[1:182] = data$y[1:182] + t_quantile*data$y[1:182]*se_cor


####### part2
var_cor_emee = matrix(c((my_plot_data[9,"SE"])^2,var_cor_2_qian,var_cor_2_qian,(my_plot_data[10,"SE"])^2),nrow=2)

calculate_se = function(x) sqrt(t(c(1,x))%*%var_cor_emee%*%c(1,x))

se_cor = sapply(data$x[183:364],FUN=calculate_se)

t_quantile <- qt(0.975, length(unique(dta$USERID)) - 1 - 2)
data$lower[183:364] = data$y[183:364] - t_quantile*data$y[183:364]*se_cor
data$upper[183:364] = data$y[183:364] + t_quantile*data$y[183:364]*se_cor


p_day<-ggplot(data=data, aes(x=x, y=y, colour=Method)) + geom_line()
p_day<-p_day+geom_ribbon(aes(ymin=lower, ymax=upper), linetype=2, alpha=0.1)+xlab("Day in Study")+ylab("Relative Risk")+
  theme_bw()+
    theme(axis.line = element_line(colour = "black"),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    panel.border = element_blank(),
    panel.background = element_blank()) +
    geom_hline(yintercept =1, linetype=2)+
    theme(axis.text=element_text(size=12),
        axis.title=element_text(size=14))#,face="bold")

```

```{r}
ggpubr::ggarrange(p,p_day,common.legend = T)
```

